---
title: "R_dataAnalysis"
author: "Ayan Dey"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Superstore Data Analysis

Today I am going to work on Superstore dataset. Analyse the data by \*\*R\*\* and get some usefull insights about the data.

firstly set up the working directory

```{r}
# to see the current working directory
getwd()
```

```{r}
# set up the working directory
setwd("C:\\Users\\growth\\Desktop\\R project")
```

```{r}
# confirmation of working directory
getwd()
```

```{r}
# importing all the  libraaries what I need the most 
 
library(tidyverse)
library(skimr)

```

```{r}
# importing the data -- I will always take the master dataset in variable = ** x **
x <- read.csv("superstore.csv")
x
```

## Explore Understand and Clean the data

```{r}
# see the dimenstion of the dataset
dim(x)
```

Number of observation is : 9996

Number of variable is : 22

```{r}
# let see all the names of the 22 variables 
names(x)
```

```{r}
# Rename sub.Category varriable name into Sub_Category
x <-x %>% rename(sub_category=Sub.Category)

```

```{r}
# confirmation
names(x)
```

```{r}
# let rename all the variable name to smaller case
names(x) <- tolower(names(x))
```

```{r}
# confirmation
names(x)
```

```{r}
# let see the structure and datatype of variables of data
glimpse(x)
```

now work with each variable

```{r}
# change datatype of order_date variable datatype into - date datatype
x$order_date<- as.Date(x$order_date)
```

```{r}
# confirmation
class(x$order_date)
```

```{r}
# change datatype of ship_date variable datatype into - date datatype
x$ship_date<- as.Date(x$ship_date)
```

```{r}
# confirmation
class(x$ship_date)
```

```{r}
# change datatype of ship_mode variable datatype into factor datatype
x$ship_mode<- as.factor(x$ship_mode)
```

```{r}
# confirmation
class(x$ship_mode)
```

```{r}
# change datatype of sales variable datatype into - Numeric datatype
x$sales<- as.numeric(x$sales)
```

NULL value introduced in sales vector

```{r}
# let ignore the NULL value for now and do the pending operation
x$sales<- as.numeric(x$sales,na.rm=TRUE)
```

```{r}
# confirmation
class(x$sales)
```

```{r}
# let see again the structure of the data
glimpse(x)
```

-   there are a x variable which make me dought so let work on it

    ```{r}
    # let see the total length of x variable
    length(x$x)
    ```

```{r}
# there have total 9996 obs. 
# let see how many NULL value are there
sum(is.na(x$x))
```

```{r}
# let see how much data hoding that variable
sum( ! is.na(x$x))
```

total 9996 values and 9990 NULL

total 6 values are there

```{r}
# let locate those values
which( ! is.na(x$x))
```

```{r}
# let see all those obs. and those values understand importancy
x[ which (!is.na(x$x)), ] 
```

**conclusion** : i can't just drop the x variable becaue it hold number 6 values

but those values are unidentified and very confusion , what the values belongs to

after confirmation I decided to drop this variable.

```{r}
# now let locate the variable
which(names(x)== "x")
```

```{r}
# let remove that  by creating another variable ( Y)
y<-x[ , -22]
```

```{r}
# confirmation
names(y)
```

now working varriable will be : [**y**]{.underline}

```{r}
print(" The new dimension is: " )
dim(y)
```

```{r}
# final confirmation 
glimpse(y)
```

all variable name , data type are set

now its time to deep dive inside the data

## NULL values

```{r}
# let check NULL values of each variable
# y <- working data
for ( i in 1:ncol(y)){
    print(paste(" null value of ",names(x[i]),"Obs. ", " index: ",i ))
     print(sum(is.na(y[i])) )
        }
```

let see each variable which have NULL values

```{r}
# let see all those data with max null
y[ , c(1:5)]
```

```{r}
# let see with out order_date and ship_date
y[ , -c(3:4)]
```

It undestood that this two column dont have much value right now to analysis , so I decided to drop this two columns .

-But also there have null in quantity(1), sales(6), discount(6) and profit ( 1) ,but I should not remove all those rows and just ignore when analysis.

```{r}
# let store the data without order_date and ship_date
y<- y[ , -c(3:4)]
```

```{r}
y
```

#### Duplicates

```{r}
# just over view the boolean matrix 
# duplicated(x)
```

```{r}
# retrive all duplicate obs.
z<-y[duplicated(y), ]
```

```{r}
# let see the duplicate values
z
write.csv(z,"see_in_LibreOffice.csv")
```

```{r}
# now remove all the duplicate obs. and make data clean
y<-y[!duplicated(y), ]
# y
```

**now the data is cleaned and ready to save and Analysis**

```{r}
# now save the cleaned file 
# write.csv(y,"superstore_cleaned.csv")
```

```{r}

```

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

-   Bullet 1
-   Bullet 2
-   Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```
